Api Gateway: Kong vs. AWS

### 2024-08-29 docs/3_kong.tex
Add the subsections of kong

\section{Kong}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-anonymous initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\subsection{Template Styles}

>>>>

\section{Kong}
Kong Gateway es una pasarela de API nativa en la nube ligera, rápida 
y flexible y un proxy inverso que le permite gestionar, configurar y 
dirigir las solicitudes a sus API.

% \url{https://www.acm.org/publications/proceedings-template}.

\subsection{API Management}
API Management

\subsection{Security}
Security

\subsection{Plugins}
Plugins

\subsection{Scalability}
Scalability
